Arc Blanc: a real time ocean simulation framework

### 2025-02-28 paper.tex
Add orcid logo
Fixed bibliography

\author{%
    David Algis\\Université de Poitiers%\\Univ. Limoges\\CNRS, XLIM, France\\Studio Nyx
    \and Berenger Bramas\\INRIA Nancy
    \and Emmanuelle Darles\\Université de Poitiers%\\ Univ. Limoges\\ CNRS, XLIM, France
    \and Lilian Aveneau\\Université de Poitiers%\\ Univ. Limoges\\ CNRS, XLIM, France
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Solid to fluid coupling}
\label{subsubsec:solidToFluidCoupling}
The simulation of the surface of water in contact with a solid body has been an active research topic for the last twenty years.
Gomez (2000) \cite{gomezInteractiveSimulationWater2000} solved the wave equation using the finite-difference method (FDM) to simulate waves on the free surface.
This method was improved by Cords and Staadt (2009) \cite{cordsRealTimeOpenWater2009} to work with moving objects.
Tessendorf (2004) \cite{tessendorfInteractiveWaterSurface2004} proposed a convolutional method.
He extended his method by using an exponential solver \cite{tessendorfEWaveUsingExponential2014}.
Yuksel (2007) \cite{yuksel2007} used a Lagrangian paradigm to model the waves as particles, which he called wave-particles.
Chentanez and Müller (2010) \cite{chentanezRealTimeSimulationLarge2010} created a hybrid solver combining Eulerian and Lagrangian approaches.
Canabal \etal (2016) \cite{canabalDispersionKernelsWater2016} improved the physical accuracy of the convolutional method by introducing a dispersion kernel.
Jeschke and Woktan (2017) \cite{jeschkeWaterWavePackets2017} took the work of C. Yuskel a bit further by introducing the notion of a wave packet, which carries information about an entire wave train.
One year later, Jeschke \etal (2018) \cite{jeschkeWaterSurfaceWavelets2018} proposed to use a wavelet transformation that discretizes the wave amplitudes as a function of space, frequency and direction.
Finally, Schreck \etal (2019) \cite{schreckFundamentalSolutionsWater2019} based their work on the method of fundamental solutions to generate ambient waves on a large scale domain interacting with complex boundaries.

@@

The buoyancy calculation presented in Section \ref{subsubsec:buoyancy} requires the full submerged volume $v_w$ of the mesh.
\Framework uses the prism approximation similarly to the approximation proposed by Bajo \etal (2020) \cite{bajoRealisticBuoyancyModel2020a}.
While Bajo \etal compute the submerged volume at the texel level, the same principle can be applied using triangles instead of texels using as they did the divergence theorem.
Specifically, $v_w$ is approximated as the sum of the prisms with bases corresponding to the triangle areas $A_i$ and heights defined by the distance $d_i$ between the triangle centers $p_i$ and the water surface $h(p_i,t)$.
Each term in the sum is weighted by the vertical component of the triangle normal $n_i^y$:
\begin{equation}
	v_w = \sum_{T_i^s} A_i d_i n_i^y.
\end{equation}
Note that this formula is correct only under the assumption that the mesh is closed.

>>>>

\author{%
    David Algis~\href{https://orcid.org/0009-0004-6033-2389}{\includegraphics[width=8pt]{Figures/ORCIDlogo}}\\Université de Poitiers%\\Univ. Limoges\\CNRS, XLIM, France\\Studio Nyx
    \and Berenger Bramas\\INRIA Nancy
    \and Emmanuelle Darles\\Université de Poitiers%\\ Univ. Limoges\\ CNRS, XLIM, France
    \and Lilian Aveneau\\Université de Poitiers%\\ Univ. Limoges\\ CNRS, XLIM, France
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Solid to fluid coupling}
\label{subsubsec:solidToFluidCoupling}
The simulation of the surface of water in contact with a solid body has been an active research topic for the last twenty years.
Gomez (2000) \cite{gomezInteractiveSimulationWater2000} solved the wave equation using the finite-difference method (FDM) to simulate waves on the free surface.
This method was improved by Cords and Staadt (2009) \cite{cordsRealTimeOpenWater2009} to work with moving objects.
Tessendorf (2004) \cite{tessendorfInteractiveWaterSurface2004} proposed a convolutional method.
He extended his method by using an exponential solver \cite{tessendorfEWaveUsingExponential2014}.
Yuksel (2007) \cite{yukselWaveParticles2007} used a Lagrangian paradigm to model the waves as particles, which he called wave-particles.
Chentanez and Müller (2010) \cite{chentanezRealTimeSimulationLarge2010} created a hybrid solver combining Eulerian and Lagrangian approaches.
Canabal \etal (2016) \cite{canabalDispersionKernelsWater2016} improved the physical accuracy of the convolutional method by introducing a dispersion kernel.
Jeschke and Woktan (2017) \cite{jeschkeWaterWavePackets2017} took the work of C. Yuskel a bit further by introducing the notion of a wave packet, which carries information about an entire wave train.
One year later, Jeschke \etal (2018) \cite{jeschkeWaterSurfaceWavelets2018} proposed to use a wavelet transformation that discretizes the wave amplitudes as a function of space, frequency and direction.
Finally, Schreck \etal (2019) \cite{schreckFundamentalSolutionsWater2019} based their work on the method of fundamental solutions to generate ambient waves on a large scale domain interacting with complex boundaries.

@@

The buoyancy calculation presented in Section \ref{subsubsec:buoyancy} requires the full submerged volume $v_w$ of the mesh.
\Framework uses the prism approximation similarly to the approximation proposed by Bajo \etal (2020) \cite{bajoRealisticBuoyancyModel2020}.
While Bajo \etal compute the submerged volume at the texel level, the same principle can be applied using triangles instead of texels using as they did the divergence theorem.
Specifically, $v_w$ is approximated as the sum of the prisms with bases corresponding to the triangle areas $A_i$ and heights defined by the distance $d_i$ between the triangle centers $p_i$ and the water surface $h(p_i,t)$.
Each term in the sum is weighted by the vertical component of the triangle normal $n_i^y$:
\begin{equation}
	v_w = \sum_{T_i^s} A_i d_i n_i^y.
\end{equation}
Note that this formula is correct only under the assumption that the mesh is closed.
